SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-13 docs/questioning.tex
add material on confidence intervals

Application attacks that involve {\sc dsl}s constitute an important
subset of the code injection problem, as {\sc dsl}s like {\sc sql} and
{\sc xml} play an significant role in the development of both web and
mobile applications. For example, many applications have interfaces
where a user enters input to interact with the application's data,
thereby interacting with the underlying Relational Database Management
System ({\sc rdbms}). This input can become part of an {\sc sql} query
and get executed on the target {\sc rdbms}. A code injection attack that
exploits the vulnerabilities of these interfaces by taking advantage
of input validation issues like incorrectly passed parameters or
incorrect type handling is called an {\sc sql} injection
attack~\cite{CERT02,MS09,HVO06,SW06}. By using similar techniques
malicious users can perform other exploits based on {\sc dsl}s
like {\sc xp}ath~\cite{SW06,CDL07,MKS09}, {\sc xml}~\cite{MSM13}
and {\sc json}~\cite{SMS13}. With this kind of attacks,
a malicious user can view sensitive information,
destroy or modify protected data, or even crash the entire
application. {\sc html} is another {\sc dsl} that can be used
for malicious purposes when an application does not properly
handle user supplied data. Based on this vulnerability
an attacker can supply valid {\sc html},
typically via a parameter value, and inject their own
content into the page. {\sc html} injection is mainly associated
with {\sc xss} defects~\cite{HNSHS12}.

@@

@@

Apart from demonstrating the value of a mechanism, good accuracy tests
may be beneficial per se, by leading to more well-designed and robust
mechanisms. Mechanisms that can be circumvented were not extensively
tested in terms of accuracy. For instance, {\sc didafit} was not
tested at all and {\sc xss-guard}'s testing involved 6 known attacks.
This also applies to some frameworks coming from the taint tracking
subcategory. It is possible that more tests during development would
have led the authors to wider improvements in design. 
%% PL: Do we have a reference in Software Engineering correlating
%% testing with better design?

@@

In order for a security tool to be used in practice it must provide
some value to the user. In particular, the value should outweigh the
cost of its use. The cost need not be directly monetary, but may be
incurred from the time required to use the tool, any inconvenience
caused, false alarms that it may raise. These costs are related to the
issues we have been investigating here: poor testing, high overhead,
unavailabilty of source, deployment difficulties, security issues.

>>>>

Application attacks that involve {\sc dsl}s constitute an important
subset of the code injection problem, as {\sc dsl}s like {\sc sql} and
{\sc xml} play an significant role in the development of both web and
mobile applications. For example, many applications have interfaces
where a user enters input to interact with the application's data,
thereby interacting with the underlying database. This input can
become part of an {\sc sql} query and get executed on the target
database. A code injection attack that exploits the vulnerabilities of
these interfaces by taking advantage of input validation issues like
incorrectly passed parameters or incorrect type handling is called an
{\sc sql} injection attack~\cite{CERT02,MS09,HVO06,SW06}. By using
similar techniques malicious users can perform other exploits based on
{\sc dsl}s like {\sc xp}ath~\cite{SW06,CDL07,MKS09}, {\sc
  xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. With this kind of
attacks, a malicious user can view sensitive information, destroy or
modify protected data, or even crash the entire application. {\sc
  html} is another {\sc dsl} that can be used for malicious purposes
when an application does not properly handle user supplied data. Based
on this vulnerability an attacker can supply valid {\sc html},
typically via a parameter value, and inject their own content into the
page. {\sc html} injection is mainly associated with {\sc xss}
defects~\cite{HNSHS12}.

@@

Even when some numbers are given, they may not be adequate.
Sensitivity and specificity are statistical measures, and as such
should be interpreted with suitable confidence intervals. There are
various methods to calculate confidence intervals, even dispensing
with the need to have large samples in order to be able to use the
central limit theorem~\cite{agresti1998,brown2001}. However, sample sizes in the single
digits are not enough to produce good intervals.

@@

Apart from demonstrating the value of a mechanism, good accuracy tests
may be beneficial per se, by leading to more well-designed and robust
mechanisms. Mechanisms that can be circumvented were not extensively
tested in terms of accuracy. For instance, {\sc didafit} was not
tested at all and {\sc xss-guard}'s testing involved 6 known attacks.
This also applies to some frameworks coming from the taint tracking
subcategory. It is possible that more tests during development would
have led the authors to wider improvements in design~\cite{Van14}.

@@

In order for a security tool to be used in practice it must provide
some value to the user. In particular, the value should outweigh the
cost of its use. The cost need not be directly monetary, but may be
incurred from the time required to use the tool, any inconvenience
caused, false alarms that it may raise. These costs are related to the
issues we have been investigating here: poor testing, high overhead,
unavailabilty of source, deployment difficulties, compromised security.
